### 2023-08-17 README.tex
Update and rename README.md to README.tex

\hypertarget{rlwe-homomorphic-encryption-scheme}{%
\section{RLWE Homomorphic Encryption
Scheme}\label{rlwe-homomorphic-encryption-scheme}}

This document provides a mathematical explanation of the RLWE (Ring
Learning With Errors) homomorphic encryption scheme. The provided Python
code demonstrates key generation, encryption, and various operations on
encrypted data.

\hypertarget{rlwe-encryption-parameters}{%
\subsection{RLWE Encryption
Parameters}\label{rlwe-encryption-parameters}}

The RLWE encryption scheme operates in a polynomial ring modulo a
polynomial modulus ( poly\_mod ). The ciphertext modulus is denoted as (
q ), and the plaintext modulus is denoted as ( t ). The encryption
scheme uses a base ( T ) for polynomial switching and a modulus ( p )
for modulus switching.

\hypertarget{parameters}{%
\subsubsection{Parameters}\label{parameters}}

The following parameters are defined:

\begin{itemize}
\tightlist
\item
  ( n ): Polynomial modulus degree
\item
  ( q ): Ciphertext modulus
\item
  ( t ): Plaintext modulus
\item
  ( T ): Base for polynomial switching
\item
  ( p ): Modulus for modulus switching
\end{itemize}

\hypertarget{key-generation}{%
\subsection{Key Generation}\label{key-generation}}

The key generation process involves generating a public key ( (a, b) )
and a secret key ( s ). The public key is used for encryption, and the
secret key is used for decryption.

\hypertarget{generating-secret-and-public-keys}{%
\subsubsection{Generating Secret and Public
Keys}\label{generating-secret-and-public-keys}}

The secret key ( s ) is a binary polynomial. The public key is generated
as follows:

\begin{itemize}
\tightlist
\item
  ( s ): Binary secret key polynomial
\item
  ( a ): Uniformly random polynomial
\item
  ( e ): Error polynomial sampled from a normal distribution
\item
  ( b ): ( \(a \cdot s - e \mod q\) )
\end{itemize}

\hypertarget{encryption}{%
\subsection{Encryption}\label{encryption}}

To encrypt a plaintext message ( m ) using the public key ( (a, b) ),
the following steps are performed:

\[
\begin{align*}
m &\equiv m \mod t \\
\text{delta} &= \frac{q}{t} \\
e1, e2 &= \text{Error polynomials sampled from a normal distribution} \\
u &= \text{Binary polynomial} \\
\text{ct} &\equiv (ct_0, ct_1) \\
ct_0 &= a \cdot u + e1 + \delta \cdot m \mod q \\
ct_1 &= b \cdot u + e2 \mod q \\
\end{align*}
\]

\hypertarget{homomorphic-operations}{%
\subsection{Homomorphic Operations}\label{homomorphic-operations}}

The RLWE encryption scheme supports various homomorphic operations, such
as addition and multiplication, on encrypted data.

\hypertarget{addition-of-ciphertext-and-plaintext}{%
\subsubsection{Addition of Ciphertext and
Plaintext}\label{addition-of-ciphertext-and-plaintext}}

To add a ciphertext ( ct ) and a plaintext ( pt ), the following
operation is performed:

\[
\begin{align*}
m &\equiv \text{pt} \mod t \\
\text{delta} &= \frac{q}{t} \\
e1 &= \text{Error polynomial} \\
\text{scaled\_m} &= \delta \cdot m \mod q \\
\text{new\_ct} &\equiv (\text{new\_ct\_0}, \text{ct\_1}) \\
\text{new\_ct\_0} &= ct_0 + \text{scaled\_m} \mod q \\
\end{align*}
\]

\hypertarget{addition-of-ciphertexts}{%
\subsubsection{Addition of Ciphertexts}\label{addition-of-ciphertexts}}

To add two ciphertexts ( ct1 ) and ( ct2 ), the following operation is
performed:

\[
\begin{align*}
\text{new\_ct} &\equiv (\text{new\_ct\_0}, \text{new\_ct\_1}) \\
\text{new\_ct\_0} &= ct1_0 + ct2_0 \mod q \\
\text{new\_ct\_1} &= ct1_1 + ct2_1 \mod q \\
\end{align*}
\]

\hypertarget{multiplication-of-ciphertext-and-plaintext}{%
\subsubsection{Multiplication of Ciphertext and
Plaintext}\label{multiplication-of-ciphertext-and-plaintext}}

To multiply a ciphertext ( ct ) by a plaintext ( pt ), the following
operation is performed:

\[
\begin{align*}
\text{scaled\_m} &= \delta \cdot m \mod q \\
\text{new\_ct} &\equiv (\text{new\_ct\_0}, \text{new\_ct\_1}) \\
\text{new\_ct\_0} &= ct_0 \cdot \text{scaled\_m} \mod q \\
\text{new\_ct\_1} &= ct_1 \cdot \text{scaled\_m} \mod q \\
\end{align*}
\]

\hypertarget{multiplication-of-ciphertexts}{%
\subsubsection{Multiplication of
Ciphertexts}\label{multiplication-of-ciphertexts}}

The multiplication of ciphertexts involves more complex steps and
relinearization keys. The provided Python code demonstrates two versions
of multiplication: version 1 and version 2.

\hypertarget{decryption}{%
\subsection{Decryption}\label{decryption}}

To decrypt a ciphertext and obtain the original plaintext message, the
following steps are performed:

\[
\begin{align*}
\text{scaled\_pt} &= ct_1 \cdot sk + ct_0 \mod q \\
\text{decrypted\_poly} &= \left\lfloor \frac{t \cdot \text{scaled\_pt}}{q} \right\rceil \mod t \\
\text{Decrypted Plaintext} &= \text{decrypted\_poly}
\end{align*}
\]

The RLWE homomorphic encryption scheme provides a powerful tool for
performing computations on encrypted data while preserving data privacy.
The scheme involves key generation, encryption, and various homomorphic
operations, making it suitable for secure computations in various
applications.

### 2023-08-17 Paper.tex
Create Paper.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{listings}

\begin{document}

\title{RLWE Homomorphic Encryption Scheme}
\author{Aidan (@CodeByAidan) | Madalina Bolboceanu (@mbolboceanu)}
\date{8/16/2023}
\maketitle

\section{Introduction}

This document provides a mathematical explanation of the RLWE (Ring Learning With Errors) homomorphic encryption scheme. The provided Python code demonstrates key generation, encryption, and various operations on encrypted data.

See more: \url{https://eprint.iacr.org/2012/144.pdf}

\section{RLWE Encryption Parameters}

The RLWE encryption scheme operates in a polynomial ring modulo a polynomial modulus $poly\_mod$. The ciphertext modulus is denoted as $q$, and the plaintext modulus is denoted as $t$. The encryption scheme uses a base $T$ for polynomial switching and a modulus $p$ for modulus switching.

\subsection{Parameters}

The following parameters are defined:

\begin{itemize}
    \item $n$: Polynomial modulus degree
    \item $q$: Ciphertext modulus
    \item $t$: Plaintext modulus
    \item $T$: Base for polynomial switching
    \item $p$: Modulus for modulus switching
\end{itemize}

\section{Key Generation}

The key generation process involves generating a public key $(a, b)$ and a secret key $s$. The public key is used for encryption, and the secret key is used for decryption.

\subsection{Generating Secret and Public Keys}

The secret key $s$ is a binary polynomial. The public key is generated as follows:

\begin{itemize}
    \item $s$: Binary secret key polynomial
    \item $a$: Uniformly random polynomial
    \item $e$: Error polynomial sampled from a normal distribution
    \item $b$: $a \cdot s - e \mod q$
\end{itemize}

\section{Encryption}

To encrypt a plaintext message $m$ using the public key $(a, b)$, the following steps are performed:

\begin{align*}
    m &\equiv m \mod t \\
    \text{delta} &= \frac{q}{t} \\
    e1 &= \text{Error polynomial} \\
    \text{scaled\_m} &= \delta \cdot m \mod q \\
    \text{new\_ct} &\equiv \text{new\_ct\_0} \\
    \text{new\_ct\_0} &= a \cdot u + e1 + \text{scaled\_m} \mod q \\
\end{align*}

\section{Homomorphic Operations}

The RLWE encryption scheme supports various homomorphic operations, such as addition and multiplication, on encrypted data.

\subsection{Addition of Ciphertext and Plaintext}

To add a ciphertext $ct$ and a plaintext $pt$, the following operation is performed:

\begin{align*}
    m &\equiv \text{pt} \mod t \\
    \text{delta} &= \frac{q}{t} \\
    e1 &= \text{Error polynomial} \\
    \text{scaled\_m} &= \delta \cdot m \mod q \\
    \text{new\_ct} &\equiv \text{new\_ct\_0} \\
    \text{new\_ct\_0} &= ct_0 + \text{scaled\_m} \mod q \\
\end{align*}

\subsection{Addition of Ciphertexts}

To add two ciphertexts $ct1$ and $ct2$, the following operation is performed:

\begin{align*}
    \text{new\_ct} &\equiv \text{new\_ct\_0} \\
    \text{new\_ct\_0} &= ct1_0 + ct2_0 \mod q \\
\end{align*}

\subsection{Multiplication of Ciphertext and Plaintext}

To multiply a ciphertext $ct$ by a plaintext $pt$, the following operation is performed:

\begin{align*}
    \text{scaled\_m} &= \delta \cdot m \mod q \\
    \text{new\_ct} &\equiv \text{new\_ct\_0} \\
    \text{new\_ct\_0} &= ct_0 \cdot \text{scaled\_m} \mod q \\
\end{align*}

\subsection{Multiplication of Ciphertexts}

The multiplication of ciphertexts involves more complex steps and relinearization keys:

\begin{align*}
    \text{new\_ct} &\equiv \text{new\_ct\_0} \\
    \text{new\_ct\_0} &= ct1_0 \cdot ct2_0 + ct1_1 \cdot ct2_1 \mod q \\
    \text{new\_ct\_1} &= ct1_0 \cdot ct2_1 + ct1_1 \cdot ct2_0 \mod q \\
\end{align*}

\section{Decryption}

To decrypt a ciphertext and obtain the original plaintext message, the following steps are performed:

\begin{align*}
    \text{scaled\_pt} &= ct_0 \cdot sk + ct_0 \mod q \\
    \text{decrypted\_poly} &= \left\lfloor \frac{t \cdot \text{scaled\_pt}}{q} \right\rceil \mod t \\
    \text{Decrypted Plaintext} &= \text{decrypted\_poly}
\end{align*}

The RLWE homomorphic encryption scheme provides a powerful tool for performing computations on encrypted data while preserving data privacy. The scheme involves key generation, encryption, and various homomorphic operations, making it suitable for secure computations in various applications.

\section{Python Code}

Thank you to the author of the original code:
\begin{itemize}
    \item Madalina Bolboceanu (\url{https://github.com/mbolboceanu})
\end{itemize}

This code is an updated version of the original code, which can be found here:
\begin{itemize}
    \item \url{https://github.com/bit-ml/he-scheme}
\end{itemize}

\pagebreak

\begin{lstlisting}[language=Python]
"""
Thank you to the author of the original code:
    - Madalina Bolboceanu (@mbolboceanu)

This code is an updated version of the original code, which can be found here:
    - https://github.com/bit-ml/he-scheme
"""

import numpy as np
from numpy.polynomial import polynomial as poly

#------Functions for polynomial evaluations mod poly_mod only------
def polymul_wm(x, y, poly_mod):
    """Multiply two polynomials
    Args:
        x, y: two polynomials to be multiplied.
        poly_mod: polynomial modulus.
    Returns:
        A polynomial in Z[X]/(poly_mod).
    """
    return poly.polydiv(poly.polymul(x, y), poly_mod)[1]

def polyadd_wm(x, y, poly_mod):
    """Add two polynomials
        Args:
            x, y: two polynomials to be added.
            poly_mod: polynomial modulus.
        Returns:
            A polynomial in Z[X]/(poly_mod).
        """
    return poly.polydiv(poly.polyadd(x, y), poly_mod)[1]
#==============================================================

# ------Functions for polynomial evaluations both mod poly_mod and mod q-----
def polymul(x, y, modulus, poly_mod):
    """Multiply two polynomials
    Args:
        x, y: two polynomials to be multiplied.
        modulus: coefficient modulus.
        poly_mod: polynomial modulus.
    Returns:
        A polynomial in Z_modulus[X]/(poly_mod).
    """
    return np.int64(
        np.round(poly.polydiv(poly.polymul(x, y) %
                              modulus, poly_mod)[1] % modulus)
    )

def polyadd(x, y, modulus, poly_mod):
    """Add two polynomials
    Args:
        x, y: two polynoms to be added.
        modulus: coefficient modulus.
        poly_mod: polynomial modulus.
    Returns:
        A polynomial in Z_modulus[X]/(poly_mod).
    """
    return np.int64(
        np.round(poly.polydiv(poly.polyadd(x, y) %
                              modulus, poly_mod)[1] % modulus)
    )
#==============================================================

# -------Functions for random polynomial generation--------
def gen_binary_poly(size):
    """Generates a polynomial with coeffecients in [0, 1]
    Args:
        size: number of coeffcients, size-1 being the degree of the
            polynomial.
    Returns:
        array of coefficients with the coeff[i] being
        the coeff of x ^ i.
    """
    return np.random.randint(0, 2, size, dtype=np.int64)

def gen_uniform_poly(size, modulus):
    """Generates a polynomial with coeffecients being integers in Z_modulus
    Args:
        size: number of coeffcients, size-1 being the degree of the
            polynomial.
    Returns:
        array of coefficients with the coeff[i] being
        the coeff of x ^ i.
    """
    return np.random.randint(0, modulus, size, dtype=np.int64)

def gen_normal_poly(size, mean, std):
    """Generates a polynomial with coeffecients in a normal distribution
    of mean mean and a standard deviation std, then discretize it.
    Args:
        size: number of coeffcients, size-1 being the degree of the
            polynomial.
    Returns:
        array of coefficients with the coeff[i] being
        the coeff of x ^ i.
    """
    return np.int64(np.random.normal(mean, std, size=size))
#==============================================================

# -------- Function for returning n's coefficients in base b ( lsb is on the left) ---
def int2base(n, b):
    """Generates the base decomposition of an integer n.
    Args:
        n: integer to be decomposed.
        b: base.
    Returns:
        array of coefficients from the base decomposition of n
        with the coeff[i] being the coeff of b ^ i.
    """
    return [n] if n < b else [n % b] + int2base(n // b, b)

# ------ Functions for keygen, encryption and decryption ------
def keygen(size, modulus, poly_mod, std1):
    """Generate a public and secret keys
    Args:
        size: size of the polynoms for the public and secret keys.
        modulus: coefficient modulus.
        poly_mod: polynomial modulus.
        std1: standard deviation of the error.
    Returns:
        Public and secret key.
    """
    s = gen_binary_poly(size)
    a = gen_uniform_poly(size, modulus)
    e = gen_normal_poly(size, 0, std1)
    b = polyadd(polymul(-a, s, modulus, poly_mod), -e, modulus, poly_mod)
    return (b, a), s

def evaluate_keygen_v1(sk, size, modulus, T, poly_mod, std2):
    """Generate a relinearization key using version 1.
        Args:
            sk: secret key.
            size: size of the polynomials.
            modulus: coefficient modulus.
            T: base.
            poly_mod: polynomial modulus.
            std2: standard deviation for the error distribution.
        Returns:
            rlk0, rlk1: relinearization key.
        """
    n = len(poly_mod) - 1
    l = np.int64(np.log(modulus) / np.log(T))
    rlk0 = np.zeros((l + 1, n), dtype=np.int64)
    rlk1 = np.zeros((l + 1, n), dtype=np.int64)
    for i in range(l + 1):
        a = gen_uniform_poly(size, modulus)
        e = gen_normal_poly(size, 0, std2)
        secret_part = T ** i * poly.polymul(sk, sk)
        b = np.int64(polyadd(
        polymul_wm(-a, sk, poly_mod),
        polyadd_wm(-e, secret_part, poly_mod), modulus, poly_mod))

        b = np.int64(np.concatenate( (b, [0] * (n - len(b)) ) )) # pad b
        a = np.int64(np.concatenate( (a, [0] * (n - len(a)) ) )) # pad a

        rlk0[i] = b
        rlk1[i] = a
    return rlk0, rlk1

def evaluate_keygen_v2(sk, size, modulus, poly_mod, extra_modulus, std2):
    """Generate a relinearization key using version 2.
        Args:
            sk: secret key.
            size: size of the polynomials.
            modulus: coefficient modulus.
            poly_mod: polynomial modulus.
            extra_modulus: the "p" modulus for modulus switching.
            st2: standard deviation for the error distribution.
        Returns:
            rlk0, rlk1: relinearization key.
        """
    new_modulus = modulus * extra_modulus
    a = gen_uniform_poly(size, new_modulus)
    e = gen_normal_poly(size, 0, std2)
    secret_part = extra_modulus * poly.polymul(sk, sk)

    b = np.int64(polyadd_wm(
        polymul_wm(-a, sk, poly_mod),
        polyadd_wm(-e, secret_part, poly_mod), poly_mod)) % new_modulus
    return b, a

def encrypt(pk, size, q, t, poly_mod, m, std1):
    """Encrypt an integer.
    Args:
        pk: public-key.
        size: size of polynomials.
        q: ciphertext modulus.
        t: plaintext modulus.
        poly_mod: polynomial modulus.
        m: plaintext message, as an integer vector (of length <= size) with entries mod t.
    Returns:
        Tuple representing a ciphertext.
    """
    m = np.array(m + [0] * (size - len(m)), dtype=np.int64) % t
    delta = q // t
    scaled_m = delta * m
    e1 = gen_normal_poly(size, 0, std1)
    e2 = gen_normal_poly(size, 0, std1)
    u = gen_binary_poly(size)
    ct0 = polyadd(
        polyadd(
            polymul(pk[0], u, q, poly_mod),
            e1, q, poly_mod),
        scaled_m, q, poly_mod
    )
    ct1 = polyadd(
        polymul(pk[1], u, q, poly_mod),
        e2, q, poly_mod
    )
    return (ct0, ct1)

def decrypt(sk, size, q, t, poly_mod, ct):
    """Decrypt a ciphertext.
    Args:
        sk: secret-key.
        size: size of polynomials.
        q: ciphertext modulus.
        t: plaintext modulus.
        poly_mod: polynomial modulus.
        ct: ciphertext.
    Returns:
        Integer vector representing the plaintext.
    """
    scaled_pt = polyadd(
        polymul(ct[1], sk, q, poly_mod),
        ct[0], q, poly_mod
    )
    decrypted_poly = np.round(t * scaled_pt / q) % t
    decrypted_poly_1 = list(decrypted_poly)
    bound = len(decrypted_poly_1)
    if bound<size:
        number_of_zeros_to_pad = size-bound
        list_to_append = [0] * number_of_zeros_to_pad
        decrypted_poly_to_return = np.append(decrypted_poly, list_to_append) #pad with 0
    else:
        decrypted_poly_to_return = decrypted_poly
    return np.int64(decrypted_poly_to_return)

#==============================================================

# ------Function for adding and multiplying encrypted values------
def add_plain(ct, pt, q, t, poly_mod):
    """Add a ciphertext and a plaintext.
    Args:
        ct: ciphertext.
        pt: integer to add.
        q: ciphertext modulus.
        t: plaintext modulus.
        poly_mod: polynomial modulus.
    Returns:
        Tuple representing a ciphertext.
    """
    size = len(poly_mod) - 1
    # encode the integer into a plaintext polynomial
    m = np.array(pt + [0] * (size - len(pt)), dtype=np.int64) % t
    delta = q // t
    scaled_m = delta * m
    new_ct0 = polyadd(ct[0], scaled_m, q, poly_mod)
    return (new_ct0, ct[1])

def add_cipher(ct1, ct2, q, poly_mod):
    """Add a ciphertext and a ciphertext.
    Args:
        ct1, ct2: ciphertexts.
        q: ciphertext modulus.
        poly_mod: polynomial modulus.
    Returns:
        Tuple representing a ciphertext.
    """
    new_ct0 = polyadd(ct1[0], ct2[0], q, poly_mod)
    new_ct1 = polyadd(ct1[1], ct2[1], q, poly_mod)
    return (new_ct0, new_ct1)

def mul_plain(ct, pt, q, t, poly_mod):
    """Multiply a ciphertext and a plaintext.
    Args:
        ct: ciphertext.
        pt: integer polynomial to multiply.
        q: ciphertext modulus.
        t: plaintext modulus.
        poly_mod: polynomial modulus.
    Returns:
        Tuple representing a ciphertext.
    """
    size = len(poly_mod) - 1
    # encode the integer polynomial into a plaintext vector of size=size
    m = np.array(pt + [0] * (size - len(pt)), dtype=np.int64) % t
    new_c0 = polymul(ct[0], m, q, poly_mod)
    new_c1 = polymul(ct[1], m, q, poly_mod)
    return (new_c0, new_c1)

def multiplication_coeffs(ct1, ct2, q, t, poly_mod):
    """Multiply two ciphertexts.
        Args:
            ct1: first ciphertext.
            ct2: second ciphertext
            q: ciphertext modulus.
            t: plaintext modulus.
            poly_mod: polynomial modulus.
        Returns:
            Triplet (c0,c1,c2) encoding the multiplied ciphertexts.
        """

    c_0 = np.int64(np.round(polymul_wm(ct1[0], ct2[0], poly_mod) * t / q)) % q
    c_1 = np.int64(np.round(polyadd_wm(polymul_wm(ct1[0], ct2[1], poly_mod), polymul_wm(ct1[1], ct2[0], poly_mod), poly_mod) * t / q)) % q
    c_2 = np.int64(np.round(polymul_wm(ct1[1], ct2[1], poly_mod) * t / q)) % q
    return c_0, c_1, c_2

def mul_cipher_v1(ct1, ct2, q, t, T, poly_mod , rlk0, rlk1):
    """Multiply two ciphertexts.
    Args:
        ct1: first ciphertext.
        ct2: second ciphertext
        q: ciphertext modulus.
        t: plaintext modulus.
        T: base
        poly_mod: polynomial modulus.
        rlk0, rlk1: output of the EvaluateKeygen_v1 function.
    Returns:
        Tuple representing a ciphertext.
    """
    n = len(poly_mod) - 1
    l = np.int64(np.log(q) / np.log(T))  #l = log_T(q)

    c_0, c_1, c_2 = multiplication_coeffs(ct1, ct2, q, t, poly_mod)
    c_2 = np.int64(np.concatenate( (c_2, [0] * (n - len(c_2))) )) #pad

    #Next, we decompose c_2 in base T:
    #more precisely, each coefficient of c_2 is decomposed in base T such that c_2 = sum T**i * c_2(i).
    Reps = np.zeros((n, l + 1), dtype = np.int64)
    for i in range(n):
        rep = int2base(c_2[i], T)
        rep2 = rep + [0] * (l + 1 - len(rep)) #pad with 0
        Reps[i] = np.array(rep2, dtype=np.int64)
    # Each row Reps[i] is the base T representation of the i-th coefficient c_2[i].
    # The polynomials c_2(j) are given by the columns Reps[:,j].

    c_20 = np.zeros(shape=n)
    c_21 = np.zeros(shape=n)
    # Here we compute the sums: rlk[j][0] * c_2(j) and rlk[j][1] * c_2(j)
    for j in range(l + 1):
        c_20 = polyadd_wm(c_20, polymul_wm(rlk0[j], Reps[:,j], poly_mod), poly_mod)
        c_21 = polyadd_wm(c_21, polymul_wm(rlk1[j], Reps[:,j], poly_mod), poly_mod)

    c_20 = np.int64(np.round(c_20)) % q
    c_21 = np.int64(np.round(c_21)) % q

    new_c0 = np.int64(polyadd_wm(c_0, c_20, poly_mod)) % q
    new_c1 = np.int64(polyadd_wm(c_1, c_21, poly_mod)) % q

    return (new_c0, new_c1)

def mul_cipher_v2(ct1, ct2, q, t, p, poly_mod, rlk0, rlk1):
    """Multiply two ciphertexts.
    Args:
        ct1: first ciphertext.
        ct2: second ciphertext.
        q: ciphertext modulus.
        t: plaintext modulus.
        p: modulus-swithcing modulus.
        poly_mod: polynomial modulus.
        rlk0, rlk1: output of the EvaluateKeygen_v2 function.
    Returns:
        Tuple representing a ciphertext.
    """
    c_0, c_1, c_2 = multiplication_coeffs(ct1, ct2, q, t, poly_mod)

    c_20 = np.int64(np.round(polymul_wm(c_2, rlk0, poly_mod) / p)) % q
    c_21 = np.int64(np.round(polymul_wm(c_2, rlk1, poly_mod) / p)) % q

    new_c0 = np.int64(polyadd_wm(c_0, c_20, poly_mod)) % q
    new_c1 = np.int64(polyadd_wm(c_1, c_21, poly_mod)) % q
    return (new_c0, new_c1)
#==============================================================
\end{lstlisting}

\end{document}

### 2023-08-17 main.py
Add files via upload

@@ -1,0 +1,69 @@
+"""
+Thank you to the author of the original code:
+    - Madalina Bolboceanu (@mbolboceanu)
+
+This code is an updated version of the original code, which can be found here:
+    - https://github.com/bit-ml/he-scheme
+"""
+
+import rlwe_he_scheme_updated as rlwe_updated
+import numpy as np
+
+if __name__ == '__main__':
+    # Scheme's parameters
+    # polynomial modulus degree
+    n = 2 ** 3
+    # ciphertext modulus
+    q = 2 ** 14
+    # plaintext modulus
+    t = 2
+    # base for relin_v1
+    T = int(np.sqrt(q))
+    # modulusswitching modulus
+    p = q ** 3
+
+    # polynomial modulus
+    poly_mod = np.array([1] + [0] * (n - 1) + [1])
+
+    # standard deviation for the error in the encryption
+    std1 = 1
+    # standard deviation for the error in the evaluateKeyGen_v2
+    std2 = 1
+
+    # Keygen
+    pk, sk = rlwe_updated.keygen(n, q, poly_mod, std1)
+
+    # EvaluateKeygen_version1
+    rlk0_v1, rlk1_v1 = rlwe_updated.evaluate_keygen_v1(sk, n, q, T, poly_mod, std1)
+
+    # EvaluateKeygen_version2
+    rlk0_v2, rlk1_v2 = rlwe_updated.evaluate_keygen_v2(sk, n, q, poly_mod, p, std2)
+
+    # Encrypting "Hello world" as binary vectors
+    plaintext = "Hello world"
+    # Convert each character to 8-bit binary
+    binary_vector = [format(ord(char), '08b') for char in plaintext]
+
+    print(f"[+] Plaintext: {plaintext}\n")
+    print(f"[+] Binary vectors: {binary_vector}\n")
+
+    # Encrypting the binary vectors
+    ciphertexts = []
+    for binary_value in binary_vector:
+        pt = [int(bit) for bit in binary_value]
+        ct = rlwe_updated.encrypt(pk, n, q, t, poly_mod, pt, std1)
+        ciphertexts.append(ct)
+
+    print(f"[+] Ciphertexts: {ciphertexts}\n")
+
+    # Decrypting the binary vectors and converting back to text
+    decrypted_binary_vectors = []
+    for ct in ciphertexts:
+        decrypted_value = rlwe_updated.decrypt(sk, n, q, t, poly_mod, ct)
[…]

### 2023-08-17 rlwe_he_scheme_updated.py

@@ -1,0 +1,394 @@
+"""
+Thank you to the author of the original code:
+    - Madalina Bolboceanu (@mbolboceanu)
+
+This code is an updated version of the original code, which can be found here:
+    - https://github.com/bit-ml/he-scheme
+"""
+
+import numpy as np
+from numpy.polynomial import polynomial as poly
+
+#------Functions for polynomial evaluations mod poly_mod only------
+def polymul_wm(x, y, poly_mod):
+    """Multiply two polynomials
+    Args:
+        x, y: two polynomials to be multiplied.
+        poly_mod: polynomial modulus.
+    Returns:
+        A polynomial in Z[X]/(poly_mod).
+    """
+    return poly.polydiv(poly.polymul(x, y), poly_mod)[1]
+
+def polyadd_wm(x, y, poly_mod):
+    """Add two polynomials
+        Args:
+            x, y: two polynomials to be added.
+            poly_mod: polynomial modulus.
+        Returns:
+            A polynomial in Z[X]/(poly_mod).
+        """
+    return poly.polydiv(poly.polyadd(x, y), poly_mod)[1]
+#==============================================================
+
+# ------Functions for polynomial evaluations both mod poly_mod and mod q-----
+def polymul(x, y, modulus, poly_mod):
+    """Multiply two polynomials
+    Args:
+        x, y: two polynomials to be multiplied.
+        modulus: coefficient modulus.
+        poly_mod: polynomial modulus.
+    Returns:
+        A polynomial in Z_modulus[X]/(poly_mod).
+    """
+    return np.int64(
+        np.round(poly.polydiv(poly.polymul(x, y) %
+                              modulus, poly_mod)[1] % modulus)
+    )
+
+
+def polyadd(x, y, modulus, poly_mod):
+    """Add two polynomials
+    Args:
+        x, y: two polynoms to be added.
+        modulus: coefficient modulus.
+        poly_mod: polynomial modulus.
+    Returns:
+        A polynomial in Z_modulus[X]/(poly_mod).
+    """
+    return np.int64(
+        np.round(poly.polydiv(poly.polyadd(x, y) %
+                              modulus, poly_mod)[1] % modulus)
+    )
+#==============================================================
+
+# -------Functions for random polynomial generation--------
+def gen_binary_poly(size):
[…]

### 2023-08-17 Paper.tex
Update Paper.tex

@@
 \usepackage{listings}
+\usepackage{hyperref}
+\usepackage{url}
+
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=blue,
+    filecolor=magenta,      
+    urlcolor=cyan,
+    pdftitle={Overleaf Example},
+    pdfpagemode=FullScreen,
+}
+\urlstyle{same}
+
+\title{RLWE Homomorphic Encryption Scheme}
+\author{
+  Aidan (\href{https://github.com}{@CodeByAidan}) \\
+  Mădălina Bolboceanu (\href{https://github.com/mbolboceanu}{@mbolboceanu}) \\
+  Miruna Roșca (\href{https://github.com/MirunaRosca}{@MirunaRosca}) \\
+  Radu Țițiu (\href{https://github.com/rtitiu}{@rtitiu})
+}
+\date{\today}
 
 \begin{document}
-
-\title{RLWE Homomorphic Encryption Scheme}
-\author{Aidan (@CodeByAidan) | Madalina Bolboceanu (@mbolboceanu)}
-\date{8/16/2023}
 \maketitle
@@
 
-See more: \url{https://eprint.iacr.org/2012/144.pdf}
+See more:
+
+\begin{itemize}
+    \item \href{https://eprint.iacr.org/2012/144.pdf}{"Somewhat Practical Fully Homomorphic"}, 
+    \item \href{https://bit-ml.github.io/blog/post/homomorphic-encryption-toy-implementation-in-python/}{"Homomorphic Encryption: a Toy Implementation in Python"}
+\end{itemize}
 
@@
 
-Thank you to the author of the original code:
+Thank you to the authors of the original code:
 \begin{itemize}
-    \item Madalina Bolboceanu (\url{https://github.com/mbolboceanu})
+    \item Mădălina Bolboceanu (\url{https://github.com/mbolboceanu})
+    \item Miruna Roșca (\url{https://github.com/MirunaRosca})
+    \item Radu Țițiu (\url{https://github.com/rtitiu})
 \end{itemize}

### 2023-08-17 api/client.py
Add files via upload

@@ -1,0 +1,52 @@
+import socket
+import numpy as np
+import os
+import sys
+
+parent_dir = os.path.dirname(os.path.abspath(__file__))
+sys.path.append(os.path.join(parent_dir, '..'))
+import rlwe_he_scheme_updated as rlwe_updated
+
+PLAINTEXT = "Testing! Hello World!"
+
+
+if __name__ == "__main__":
+    host = 'localhost'
+    port = 12345
+
+    n = 2 ** 3
+    q = 2 ** 14
+    t = 2
+
+    T = int(np.sqrt(q))
+    p = q ** 3
+    poly_mod = np.array([1] + [0] * (n - 1) + [1])
+    std1 = 1
+    std2 = 1
+
+    pk, sk = rlwe_updated.keygen(n, q, poly_mod, std1)
+
+    client_socket = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
+    client_socket.connect((host, port))
+
+    # Send the secret key to the server
+    sk_bytes = sk.tobytes()
+    client_socket.sendall(sk_bytes)
+    print("Sent secret key to server")
+
+    binary_vector = [format(ord(char), '08b') for char in PLAINTEXT]
+
+    ciphertexts = []
+    for binary_value in binary_vector:
+        pt = [int(bit) for bit in binary_value]
+        ct = rlwe_updated.encrypt(pk, n, q, t, poly_mod, pt, std1)
+        ciphertexts.append(ct)
+
+    for ct in ciphertexts:
+        ct_combined = np.concatenate((ct[0], ct[1]))
+        client_socket.sendall(ct[0].tobytes())
+        client_socket.sendall(ct[1].tobytes())
+
+    print("Sent ciphertexts to server")
+
+    client_socket.close()

### 2023-08-17 api/server.py

@@ -1,0 +1,104 @@
+import socket
+import numpy as np
+import os
+import sys
+import datetime
+
+parent_dir = os.path.dirname(os.path.abspath(__file__))
+sys.path.append(os.path.join(parent_dir, '..'))
+
+import rlwe_he_scheme_updated as rlwe_updated
+
+def decrypt_ciphertexts(ciphertexts, sk, n, q, t, poly_mod):
+    decrypted_binary_vectors = []
+    for ct in ciphertexts:
+        ct_combined = np.concatenate((ct[0], ct[1]))
+        decrypted_value = rlwe_updated.decrypt(
+            sk, n, q, t, poly_mod, ct_combined)
+        decrypted_binary_vectors.append(decrypted_value)
+    return ''.join(
+        [
+            chr(int(''.join(map(str, binary_vector)), 2))
+            for binary_vector in decrypted_binary_vectors
+        ]
+    )
+
+
+if __name__ == "__main__":
+    host = 'localhost'
+    port = 12345
+
+    n = 2 ** 3
+    q = 2 ** 14
+    t = 2
+
+    poly_mod = [1] + [0] * (n - 1) + [1]
+
+    server_socket = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
+    server_socket.bind((host, port))
+    server_socket.listen()
+
+    print("Server is listening for incoming connections...")
+
+    client_socket, _ = server_socket.accept()
+
+    # Receive the secret key from the client
+    sk_bytes = client_socket.recv(4096)
+    sk = np.frombuffer(sk_bytes, dtype=np.int64)
+
+    received_data = b''
+    while True:
+        if data := client_socket.recv(4096):
+            received_data += data
+
+        else:
+            break
+    print("Received data")
+
+    ciphertexts = []
+    chunk_size = n * 8 * 2  # 8 * 8 * 2 = 128 bytes
+    for i in range(0, len(received_data), chunk_size):
+        ct_part1 = np.frombuffer(received_data[i:i + n * 8], dtype=np.int64)
+        ct_part2 = np.frombuffer(
+            received_data[i + n * 8:i + 2 * n * 8], dtype=np.int64)
+        ciphertexts.append((ct_part1, ct_part2))
+    print(ciphertexts)
+
+    decrypted_binary_vectors = []
+
+    for ct in ciphertexts:
+        decrypted_value = rlwe_updated.decrypt(sk, n, q, t, poly_mod, ct)
[…]

### 2023-08-18 api/startup.sh
Add files via upload

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+# Start the server script in the background
+python server.py &
+
+# Wait for a couple of seconds
+sleep 2
+
+# Run the client script
+python client.py
